Quality Assesment of OpenStreetMap Footpath Data for 3D City Modelling

### 2020-05-10 report/report.tex
Update todo
Colliding edges per feature, calculations

% TODO: Reformat 8.3 to show the suggested algorithms in a list, with figure references
% TODO: Figure showing how turning function is calculated from edges and angles

@@

%TODO: Calculations here
***\% of feautures collide and ***\% of edges.
This means that for each colliding road, on average ***\% of its edges will be intersecting some other feature, thus bearing responsibility for the collision.
In total there are ***\% feautures ***\% edges, meaning that each feature on average is contructed out of *** edges.
Thus the percentage of edges colliding per road is on average ***\%.
The conclusion is that most often, a small part of a road is colliding, and will need correction.
Visual inspection of the cases where roads collide with other features has supported this.

>>>>

% TODO: Reformat 8.3 to show the suggested algorithms in a list, with figure references

@@

3189 features collide and 7330 of edges.
This means that for each colliding road, on average 2.3 of its edges will be intersecting some other feature, thus bearing responsibility for the collision.
In total there are 26473 feautures 6382579 edges, meaning that each feature on average is contructed out of 241 edges.
Thus the percentage of edges colliding per road is on average roughly 0.95\%.
A similar calculation for the number of features that could not be corrected by translation yields that the number of colliding edges per feature is on average 1.2, and that the percentage of colliding edges per feature is 0.49\%.
The conclusion is that most often, a small part of a road is colliding, and will need correction.
Visual inspection of the cases where roads collide with other features has supported this.
